---
title: "Immigration_plots"
author: "Smriti"
date: "2024-06-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(modelsummary)
library(stm)
library(here)

immigration_data <- read_csv("Immigrant.csv", skip = 3, col_names = c('date','report_crime','immigrant_crime','immigrant_welfare'))


immigration_data <- immigration_data%>%
  mutate(month = parse_date(date, "%Y-%m")) %>% 
  mutate(president = as.factor(ifelse(year(month) <= 2008, "Bush", ifelse(year(month) >= 2017, "Trump", "Obama"))))


immigration_data %>% 
  pivot_longer(names_to = "trend_type", values_to = "trends", cols = contains("_")) %>%
  ggplot(aes(x=month, y = trends,color = president)) + geom_point(alpha = 0.3) + 
  geom_smooth(method = lm, se = F) +
  facet_wrap(~trend_type, dir = "v")
```
Creating Table 3:

```{r}
table3 <- immigration_data %>% 
  mutate(is_trump = president == "Trump", is_bush = president == "Bush") 

models <- list(
report_crime_model = lm(report_crime ~ month + is_trump + is_bush, data = table3),
immigrant_crime_model = lm(immigrant_crime ~ month + is_trump + is_bush, data = table3),
immigrant_welfare_model = lm(immigrant_welfare ~ month + is_trump + is_bush, data = table3))

msummary(models, output = 'markdown')
```
```{r}
table3 %>% 
  add_predictions(models[["report_crime_model"]]) %>% 
  ggplot(aes(x=month, y = report_crime,color = president)) + geom_point(alpha = 0.3) + 
  geom_smooth(method = lm, se = F) +
  geom_line(aes(y=pred), line_type= "dashed")

table3 %>%
  add_predictions(models[["immigrant_crime_model"]]) %>%
  ggplot(aes(x=month, y = immigrant_crime,color = president)) + geom_point() + 
  geom_smooth(method = lm, se = F) +
  geom_line(aes(y=pred), line_type= "dashed")

table3 %>% 
  add_predictions(models[["immigrant_welfare_model"]]) %>%
  ggplot(aes(x=month, y = immigrant_welfare,color = president)) + geom_point() + 
  geom_smooth(method = lm, se = F) +
  geom_line(aes(y=pred), line_type= "dashed")
```
```{r}
library(stm)
load("TopicModel.RData")
document_topics <- make.dt(immigrFit, meta = out$meta)
topic_terms <- t(exp(immigrFit$beta$logbeta[[1]]))
rownames(topic_terms) <- out$vocab
colnames(topic_terms) <- sprintf("Topic%d", 1:ncol(topic_terms))

document_topics <- document_topics %>% 
  mutate(date = ymd(date))

sections <- document_topics %>% 
  filter(time == "pre-election") %>% 
  arrange(date) %>% 
  slice_tail(n=1) %>% 
  pull(date)

sections2 <- document_topics %>% 
  filter(time == "post-election") %>% 
  arrange(date) %>% 
  slice_head(n=1) %>% 
  pull(date)

document_topics %>% 
  mutate(month = floor_date(date, "month")) %>% 
  group_by(month, channel, time) %>% 
  summarize(num_segments = n()) %>% 
  ggplot(aes(x=month,y = num_segments, color = channel)) + 
  geom_point() +
  geom_smooth(aes(group=interaction(channel,time)), se = F) +
  geom_vline(aes(xintercept = sections), linetype = "dashed") +
  geom_vline(aes(xintercept = sections2), linetype = "dashed") +
  scale_color_manual(values = c("magenta", "red", "blue"))

```

We see a similar kind of result.

```{r}
document_topics %>% 
  mutate(month = floor_date(date, "month")) %>% 
  group_by(month, channel, time) %>% 
  summarize(proportion1 = sum(Topic1), proportion3 = sum(Topic3), crime_coverage = proportion1+proportion3) %>% 
  ggplot(aes(x=month,y = crime_coverage, color = channel)) + 
  geom_point() +
  geom_smooth(aes(group=interaction(channel,time)), se = F) +
  geom_vline(aes(xintercept = sections), linetype = "dashed") +
  geom_vline(aes(xintercept = sections2), linetype = "dashed") +
  scale_color_manual(values = c("magenta", "red", "blue"))

document_topics %>% 
  mutate(month = floor_date(date, "month")) %>% 
  group_by(month, channel, time) %>% 
  summarize(welfare = sum(Topic13)) %>% 
  ggplot(aes(x=month,y = welfare, color = channel)) + 
  geom_point() +
  geom_smooth(aes(group=interaction(channel,time)), se = F) +
  geom_vline(aes(xintercept = sections), linetype = "dashed") +
  geom_vline(aes(xintercept = sections2), linetype = "dashed") +
  scale_color_manual(values = c("magenta", "red", "blue"))

```
```{r}
table4 <- document_topics %>% 
  mutate(month = floor_date(date, "month")) %>% 
  group_by(month, time) %>% 
  summarize(proportion1 = sum(Topic1), proportion3 = sum(Topic3), crime_coverage = proportion1 + proportion3, welfare = sum(Topic13), num_segments = n()) %>% 
  mutate(trump_admin = time == "post-election") %>% 
  inner_join(immigration_data, by = "month")

lm(report_crime ~ num_segments+ crime_coverage + welfare + trump_admin + month, data = table4) %>% 

msummary(output = 'markdown')
```
```{r}
report_data <- read_csv('project/from_replication_files/google_trends_report.csv') %>% 
  rename(report_trend = search)
crime_data <- read_csv('project/from_replication_files/google_trends_crime.csv') %>% 
  rename(crime_trend = search)
welfare_data <- read_csv('project/from_replication_files/google_trends_welfare.csv') %>% 
  rename(welfare_trend = search)

trend_data_given <- report_data %>% 
  inner_join(crime_data, by = c("year", "month")) %>% 
  inner_join(welfare_data, by = c("year", "month")) %>% 
  mutate(month = paste(year,month), month = parse_date(month, "%Y %m")) %>% 
  mutate(president = as.factor(ifelse(year(month) <= 2008, "Bush", ifelse(year(month) >= 2017, "Trump", "Obama"))))

trend_data_given %>% 
  pivot_longer(names_to = "trend_type", values_to = "trends", cols = contains("_")) %>%
  ggplot(aes(x=month, y = trends,color = president)) + geom_point(alpha = 0.3) + 
  geom_smooth(method = lm, se = F) +
  facet_wrap(~trend_type, dir = "v")

```
```{r}
table3 <- immigration_data %>% 
  mutate(is_trump = president == "Trump", is_bush = president == "Bush") 

models <- list(
report_crime_model = lm(report_crime ~ month + is_trump + is_bush, data = table3),
immigrant_crime_model = lm(immigrant_crime ~ month + is_trump + is_bush, data = table3),
immigrant_welfare_model = lm(immigrant_welfare ~ month + is_trump + is_bush, data = table3))

msummary(models, output = 'markdown')
table4 <- document_topics %>% 
  mutate(month = floor_date(date, "month")) %>% 
  group_by(month, time) %>% 
  summarize(proportion1 = sum(Topic1), proportion3 = sum(Topic3), crime_coverage = proportion1 + proportion3, welfare = sum(Topic13), num_segments = n()) %>% 
  mutate(trump_admin = time == "post-election") %>% 
  inner_join(immigration_data, by = "month")

lm(report_crime ~ num_segments+ crime_coverage + welfare + trump_admin + month, data = table4) %>% 

msummary(output = 'markdown')
```
```{r}
gt_report_daily_data <- read_csv("gt_report_daily.csv")

table_daily_data <- document_topics %>% 
  group_by(date, time) %>% 
  summarize(proportion1 = sum(Topic1), proportion3 = sum(Topic3), crime_coverage = proportion1 + proportion3, welfare = sum(Topic13), num_segments = n()) %>% 
  mutate(trump_admin = time == "post-election", month_of_year = month(date, label = T), 
    day_of_week = wday(date, label=T)) %>% 
  inner_join(gt_report_daily_data, by = "date")

lm(search ~ num_segments+ crime_coverage + welfare + trump_admin + date + day_of_week + month_of_year, table_daily_data) %>% 
msummary(output = 'markdown')

lm(search_adj ~ num_segments+ crime_coverage + welfare + trump_admin + date + day_of_week + month_of_year, table_daily_data) %>%
msummary(output = 'markdown')
```
```{r}
report_data <- read_csv("report.csv", skip = 3, col_names = c('date','count1'))
crime_data <- read_csv("crime.csv", skip = 3, col_names = c('date','count2'))
welfare_data <- read_csv("welfare.csv", skip = 3, col_names = c('date','count3'))

trend_data_new <- report_data %>% 
  inner_join(crime_data, by = c("date")) %>% 
  inner_join(welfare_data, by = c("date")) %>% 
  mutate(month = parse_date(date, "%Y-%m")) %>% 
  mutate(president = as.factor(ifelse(year(month) <= 2008, "Bush", ifelse(year(month) >= 2017, "Trump", "Obama"))))

trend_data_new %>% 
  pivot_longer(names_to = "trend_type", values_to = "trends", cols = contains("count")) %>%
  ggplot(aes(x=month, y = trends,color = president)) + geom_point(alpha = 0.3) + 
  geom_smooth(method = lm, se = F) +
  facet_wrap(~trend_type, dir = "v")


```
We get a different result for welfare because we can see that in actual data, welfare search aftee Trump goes up, where here, conducting reserach individually, makes welfare search line gradually decrease.

#Extension:

The paper says: "We also expect that when the Trump administration receives media coverage for anti-immigrant rhetoric or policies, we will see an uptick in reporting searches. However, we do not expect a discontinuity in  reporting searches immediately after the 2016 election, nor do we expect media coverage of candidate Trump’s anti-immigrant rhetoric to generate more reporting searches. Neither candidate Trump nor president-elect Trump had the power to change immigration policy before his inauguration, so his anti-immigrant positions should not increase interest in reporting" (5-6). Smriti and I are skeptical of this claim, which the paper doesn't seem to actually prove, so we are going to investigate it and see if we find any discontinuities, and whether coverage of Candidate Trump also increases the amount of reporting.

```{r}
table_trump <- document_topics %>% 
  mutate(month = floor_date(date, "month")) %>% 
  group_by(month, channel, time, trump) %>% 
  summarize(proportion1 = sum(Topic1), proportion3 = sum(Topic3), crime_coverage = proportion1 + proportion3, welfare = sum(Topic13), num_segments = n()) %>% 
  mutate(trump_admin = time == "post-election") %>% 
  inner_join(immigration_data, by = "month")

lm(report_crime ~ num_segments+ crime_coverage + welfare + trump_admin + time * trump + month, table_trump) %>% 

msummary(output = 'markdown')
```
```{r}
discontinuity_data <- gt_report_daily_data %>% 
   mutate(arbitrary_before = date > ymd("2016-09-01"), after_election = date >  ymd("2016-11-8"), after_inaugration = date> ymd("2017-01-20"), arbitrary_after = date >ymd("2017-04-01")) %>% 
  filter(date >= ymd("2014-01-01")) 

discontinuity_data %>% 
  pivot_longer(c(arbitrary_before,after_election, after_inaugration, arbitrary_after), names_to = "split_location", values_to = "split_values") %>% 
  filter(date >= ymd("2014-01-01")) %>% 
  ggplot(aes(x=date, y = search_adj, color = split_values)) +
  geom_point(alpha = 0.05) +
  geom_smooth(method = lm, formula = y~x, se = F) +
  facet_wrap(~split_location)
```
So we divided the splits to make the deductions more stronger, the data after the election showed a large discontinuity. 

```{r}
list(
  lm(search_adj ~ date + arbitrary_before, discontinuity_data),
  lm(search_adj ~ date + after_election, discontinuity_data),
  lm(search_adj ~ date + after_inaugration, discontinuity_data),
  lm(search_adj ~ date + arbitrary_after, discontinuity_data)
) %>% 

msummary(output = 'markdown')
```

